Describing the C-space of asynchronous periodic task using DIT

### 2013-07-22 dit-paper_ieee.tex
minor changes

Abstract models for real-time systems often require the determination of the (worst-case) computation time of a job, a value highly dependent on the platform on which the application will be deployed.\\

The \emph{C-space} of a real-time system is, intuitively, the set of execution times value for which this system would be feasible. A precise and efficient description of its C-space would allow to quickly decide if a system is feasible on a given platform.\\

This section review the current description of the C-space of synchronous constrained systems, mostly studied by \cite{george2009characterization}.

@@

  We consider a discrete time and systems of periodic concrete tasks with constrained deadline on uniprocessor platform, where each task $\tau_i$ is represented by a tuple $(O_i, C_i, D_i, T_i)$ where $O_i$ is the offset value, $C_i$ the execution time, $D_i$ the relative deadline and $T_i$ the period. The constrained deadline property implies that $D_i \leq T_i \; \forall i$. In the following, we differentiate between \emph{synchronous systems} (where $O_i = 0 \; \forall i$) and \emph{asynchronous systems} (which are not synchronous).\\

  For those systems, the \emph{Earliest Deadline First} (EDF) algorithm, in which jobs are prioritized according to their absolute deadline, has been shown to be optimal [citation needed], that is it schedules any feasible system.\\

  Furthermore, the following notations are used:
  \begin{itemize}
    \item $\tau = (\tau_0, \cdots, \tau_{n-1})$
    \item $H = \operatorname{lcm}(T_0, \cdots, t_{n-1})$
    \item $O_{max} = \max (O_0, \cdots, O_{n-1})$
    \item An \emph{idle time} is an instant $t$ at which each job that arrived strictly before $t$ has finished its execution.
    \item The interval between the initial time and the first idle time is called the \emph{busy period}.
  \end{itemize}

@@

  \begin{definition}
  The \textbf{demand-bound function (DBF)}
  \cite{baruah1999generalized, baruah1990algorithms} defined for a task set
  $\tau$ and noted $\dbf{t_1, t_2}$, is equal to the maximal cumulated execution time of jobs of $\tau$ contained in the interval $[t_1, t_2]$.
  \end{definition}

@@

\nocite{*}
\bibliographystyle{latex8}
\bibliography{dit-paper}

>>>>

Abstract models for real-time systems often require the determination of the
(worst-case) computation time of a job (WCET), a value highly dependent on the
platform on which the application will be deployed.\\

The \emph{C-space} of a real-time system is, intuitively,
the set of WCET values for which this system would be feasible. A
precise and efficient description of its C-space would allow to quickly decide
if a system is feasible on a given platform.\\

In this section the current description of the C-space of synchronous
constrained systems is reviewed, mostly through
\cite{george2009characterization}.

@@

We consider a discrete timeline and systems comprised of periodic concrete
tasks with constrained deadlines on uniprocessor platforms, where each task
  $\tau_i$ is represented by a tuple $(O_i, C_i, D_i, T_i)$ where $O_i$ is the offset value,
  $C_i$ the WCET, $D_i$ the relative deadline and $T_i$ the period.
  The constrained deadline property implies that $D_i \leq T_i \; \forall i$. In
  the following, we differentiate between \emph{synchronous systems} (where $O_i
  = 0 \; \forall i$) and \emph{asynchronous systems} (which are not synchronous).\\

  For those systems, the \emph{Earliest Deadline First} (EDF) algorithm, in
  which jobs are prioritized according to their absolute deadline, has been
  shown to be optimal \cite{liu1973scheduling}, which means it
  correctly schedules any feasible system within that group.\\

  Furthermore, the following notations are used:
  \begin{itemize}
    \item $\tau = \{\tau_0, \cdots, \tau_{n-1}\}$
    \item $H = \operatorname{lcm}(T_0, \cdots, t_{n-1})$
    \item $O_{max} = \max (O_0, \cdots, O_{n-1})$
    \item An \emph{idle time} is an instant $t$ at which each job that arrived
    \emph{strictly} before $t$ has finished its execution.
    \item A \emph{busy period} is a time interval during which there is always
    at least one job available and not finished in the system and maximal
    (in interval length) with this property. Any busy period starts and ends
    with an idle time.
    \item The interval between the initial time and the first
    idle time is called the \emph{first busy period}.
  \end{itemize}

@@

  \begin{definition}
  The \textbf{demand-bound function (DBF)}
  \cite{baruah1999generalized, baruah1990algorithms} defined for a task set
  $\tau$ and noted $\dbf{t_1, t_2}$, is equal to the maximal cumulated execution
  time of jobs of $\tau$ contained in the closed interval $[t_1, t_2]$.
  \end{definition}

@@

% \nocite{*}
\bibliographystyle{latex8}
\bibliography{dit-paper}
